aaaa

### 2023-11-01 outputs/paper/paper.qmd
Update the introduction
Second draft

On May 23rd, the WHO chief Tedros announced that the COVID-19 ends and COVID-19 is no longer regarded as a global threat. At this point, the epidemic that lasted for three years has officially ended. During the three years, nearly 7.6 billion people got infected and about 6.9 million people lost their lives. With that said, the US seems to be one of the countries that had influenced by COVID-19 most, there was about 1.1 million deaths and 104 million infections. The mortality rate of COVID-19 in US is about 341 per 100,000, which is significantly higher than other western developed countries. Meanwhile, the COVID was entirely occured in the Biden's term and next year will be the Federal Election. It is worth to know how the COVID deaths is related to the politics and how to recover it, especially that we are now at the post-pandemic period.

In this paper, I aim to find the variations of death rate across different counties, to see how the counties with different socio-economic factors were affected by COVID differently. In addition, I will also include the political factors, to see whether the party that counties voted for will display any differences on COVID death. There are three primary data sources which are American Community Survey collecting the socio-economic information for each county, the John-Hopkins public data for COVID cases and deaths for each county and the 2020 US Federal Election from Fox News. With capturing this variations, it can help us to access the inequality of mortality caused by COVID across different counties. Besides, people living at each county will also know whether their political reference will affect the death rate, this can significantly judge them about how they will vote on the 2024 Federal Election.

There will be four main parts in this paper: Data, Models, Results, Discussion and Conclusion. In the Data part, I will introduce the data used in this paper and high light the key variables. The Models and Results session will introduce the model that will be used in this paper and the results from it. Moreover, the results will be interpreted and provide the insights about COVID deaths rate. Lastly, I will conclude the entire paper and discussion the limitations and drawbacks.

>>>>

On May 23rd, the WHO's Director-General, Dr. Tedros Adhanom Ghebreyesus, announced the end of the COVID-19 pandemic, declaring that the virus was no longer considered a global threat. This marked the official end of the pandemic that spanned three years. Over this period, nearly 7.6 billion people got infected, and approximately 6.9 million succumbed to the disease. The US seems to be one of the countries that have been influenced by COVID-19 the most, with about 1.1 million dead and 104 million infections. The mortality rate of COVID-19 in the US is about 3.41 per 1,000, which is significantly higher than in other western developed countries. Interestingly, the pandemic began around the time of the 2020 Federal Election and unfolded entirely during President Biden's term. As another Federal Election looms next year, it is worth knowing how the COVID deaths are related to socio-economic indicators. There's also speculation about the role of political preferences. Analyzing these connections could provide insights to better prepare for and prevent future health crises, especially as we navigate the post-pandemic period.

To understand and explore the COVID death rate, I will use five data sets from three different sources. American Community Survey [citation] collects the socio-economic information for each county, such as the mean household income. The Johns Hopkins University's public dataset [citation] presents data on COVID-19 cases and deaths by county. Regarding electoral data, Fox News and The New York Times have comprehensive records of the 2020 US Federal Election, providing the vote counts for each party across all counties. These data can help us to assess the inequality of mortality caused by COVID across different countries.

My analysis will be focused on the variations of death rates across different counties to see how the counties with different socio-economic factors will affect the COVID-19 deaths. Moreover, I will incorporate a political dimension, especifically the voting rate in support of the Republican party in each county, to see whether a higher proportion of Republican voters in a county correlates with the COVID-19 death rate. Through this paper, I aim to construct a model where the COVID-19 death rate is the dependent variable and includes only those predictors that are statistically significant. This study can help US citizens understand the factors affecting the death rate and inform their voting decisions in 2024.

There will be four main parts in this paper. In the Data part, I will introduce the data used in this paper and highlight the key variables. The Methods and Results parts will introduce the methods used in this paper and the corresponding results. Moreover, the results will be interpreted and provide insights about the COVID-19 death rate. Lastly, I will conclude the entire paper and discuss the limitations and drawbacks.
